---
title: "Presentation title"
subtitle: "Presentation subtitle"
author: "Author Name"
institute: "NHS Organisation"
date: "Presentation Date"
output:
  xaringan::moon_reader:
    css: 
      - default
      - css/nhsr.css
      - css/nhsr-fonts.css
    lib_dir: libs
    seal: false
    self_contained: TRUE
    nature:
      highlightStyle: googlecode
      highlightLines: true
      highlightLanguage: ["r"]
      countIncrementalSlides: false
      ratio: "16:9"
    includes:
      after_body: [css/insert-logo.html]
---

```{r setup, include = FALSE}
library(knitr)
library(tidyverse)
library(nhsrtheme)
# set default options
opts_chunk$set(echo = FALSE,
               fig.width = 7.252,
               fig.height = 4,
               dpi = 300,
               dev.args = list(type = "cairo"))

# uncomment the following lines if you want to use the NHS-R theme colours by default
# scale_fill_continuous <- partial(scale_fill_nhs, discrete = FALSE)
# scale_fill_discrete <- partial(scale_fill_nhs, discrete = TRUE)
# scale_colour_continuous <- partial(scale_colour_nhs, discrete = FALSE)
# scale_colour_discrete <- partial(scale_colour_nhs, discrete = TRUE)
```

class: title-slide, left, bottom

# `r rmarkdown::metadata$title`
----
## **`r rmarkdown::metadata$subtitle`**
### `r rmarkdown::metadata$author`
### `r rmarkdown::metadata$date`

---
class: inverse, middle, center

# An inverse slide

Often used for transitions

---

# Bullets and text color

--

* first point

--

* second point

--

* third point

--

-----

You can emphasize text with color:

* .blue[Blue]
* .green[Green]
* .pink[Pink]
* .red[Red]
* .warmyellow[Warm Yellow]

--

And make it **bold** or _italicized_ using Markdown:

* .blue[**Bold** or _italicized_]
* .green[**Bold** or _italicized_]
* .pink[**Bold** or _italicized_]
* .red[**Bold** or _italicized_]
* .warmyellow[**Bold** or _italicized_]

---

# Line highlighting

An example of using the trailing comment `#<<` to highlight lines:

### Code

````markdown
`r ''````{r tidy=FALSE}
library(ggplot2)
ggplot(mtcars) + 
  aes(mpg, disp) + 
  geom_point() +   #<<
  geom_smooth()    #<<
```
````

### Output

```{r tidy=FALSE, eval=FALSE, echo=TRUE}
library(ggplot2)
ggplot(mtcars) + 
  aes(mpg, disp) + 
  geom_point() +   #<<
  geom_smooth()    #<<
```
